Main Analyses

### 2016-02-23 Rmd/figures.Rmd
Separated figures onto new Rmd, and completely analysis up through weight selection as function of range in data relative to worst case.

setwd("~/Dropbox/publications/zambiaToff/private/zambiaToff/")
p_root <- getwd()
p_demand <- fp(p_root, "external/input_devel/demand/")
p_mod <- fp(p_root, "agroEcoTradeoff")
p_moddat <- fp(p_mod, "external/data/ZA")
p_figures <- full_path(p_root, "paper/figures/")
p_other <- fp(p_root, "external/input_devel/other/")
p_roads <- fp(p_root, "external/input_devel/roads")
p_roads2 <- paste0("/Users/lestes/Dropbox/data/zari/infrastructure/zambia/", 
                   "rda_dump/Final Shape files RDA/")
p_out <- fp(p_mod, "external/output")
```

```{r, eval = FALSE}
# roads
mgrid <- raster(fp(p_moddat, "ZA-mask.tif"))
load(fp(p_mod, "external/data/ZA/parks_roads.rda"))
zamroads <- readOGR(fp(p_roads, "osmroads/zamroadsfp.shp"), 
                    layer = "zamroadsfp")
roads <- zamroads
save(pas, roads, zambia, 
     file = full_path(p_mod, "external/data/ZA/parks_roads.rda"))

@@

## Demand
Following the example of Gasparri et al (2015), who report demand and area planted trends for soybean in Southern Africa (9 countries) between 2000-2013, we use the production trends for both maize and soybean for the periods for 2000-2014 to calculate scenario for production increases by extrapolating linearly from recent trends in production for each crop between 2014 and 2050. We took an average of both the 2000-2014 as well as the 2005-2014 trends, which show larger rates of gain, which may reflect the more recent agricultural development interests (cite).

```{r, eval = FALSE}
# fao stats for maize area harvested
ha <- data.table(read_excel(fp(p_demand, "fao-saf-maize-soybean-ha.xlsx")))
prod <- data.table(read_excel(fp(p_demand, "fao-saf-maize-soybean-prod.xlsx")))

# countries included in Gasparri et al (2015)
gasparri <- unique(ha$AreaName)[c(1:2, 7:8, 13, 15, 17, 19, 22)]
har <- ha[AreaName %in% gasparri]
setkey(har, "AreaName")
prodr <- prod[AreaName %in% gasparri]
setkey(prodr, "AreaName")
# prodr[AreaName == "Zambia" & Year %in% 2012:2014, mean(Value), by = ItemName]
# har[, unique(AreaName)]; prodr[, unique(AreaName)]

haregion <- har[, mean(Value), by = .(ItemName, Year)]
ha_rates <- sapply(c("Maize", "Soybeans"), function(i) {
  haregion[ItemName == i, coef(lm(V1 / V1[1] ~ Year))[2]]
})
prodregion <- prodr[, mean(Value), by = .(ItemName, Year)]
prod_rates <- sapply(c("Maize", "Soybeans"), function(i) {
  prodregion[ItemName == i, coef(lm(V1 / V1[1] ~ Year))[2]]
})
# prodregion[ItemName == "Maize", plot(Year, V1)]
# prodregion[ItemName == "Soybeans", plot(Year, V1)]
# haregion[ItemName == "Maize", plot(Year, V1)]
# haregion[ItemName == "Soybeans", plot(Year, V1)]

ha_rates05 <- sapply(c("Maize", "Soybeans"), function(i) {
  haregion[ItemName == i & Year > 2004, coef(lm(V1 / V1[1] ~ Year))[2]]
})
prod_rates05 <- sapply(c("Maize", "Soybeans"), function(i) {
  prodregion[ItemName == i & Year > 2004, coef(lm(V1 / V1[1] ~ Year))[2]]
})
# (1 + prod_rates05[2] * 13) * prodregion[ItemName == "Soybeans", V1]

allrates <- rbind(1 + ha_rates * (2050-2014), 1 + prod_rates * (2050-2014), 
                  1 + ha_rates05 * (2050-2014), 1 + prod_rates05 * (2050-2014))

# a <- 2
# b <- 10
# (a + sum((b - a) / (2010 - 2000) * rep(1, 10))) / a
# ((b - a) / (2010 - 2000))
# 5 * 100
# targets(c("maize" = 2), 10, 2)

round(colMeans(allrates[c(2, 4), ]), 1)  ## by production
round(colMeans(allrates[c(1, 3), ]), 1)  ## by area harvested
round(colMeans(allrates), 1)  ## averaged across production and area harvested
```

### Yield gap closure on existing land

We use the production based target as our potential scenario for Zambia.  Next is to factor in an assumption for how much demand will be met by closing current yield gaps
```{r}
setwd(p_mod)
path <- "external/data/ZA"
# load(fp(path, "currprod.rda"))
# load("~/Dropbox/projects/agroEcoTradeoff/external/data/ZA/currprod.rda")
# save(currprod, file = fp(path, "currprod.rda"))
cp <- c("maize" = 2912004, "soy" = 203732)

# gap closing function
gapper <- function(cp, gaps, pct) ((((cp * gaps) - cp) * pct) + cp) / cp

# Current gaps
mzgap <- 4.43 / 2.3 
soygap <- 3.4 / 2

# assume 50% closed on current land
g <- gapper(cp, c(mzgap, soygap), 0.25)

# targets given g
targ <- c("maize" = 3, "soy" = 9)
# targ <- c("maize" = 3.2, "soy" = 8.7)
targs <- targets(targ, cp, g)

@@

Running the model individually for each crop. This currently entails updating and the `currprod.rda` file, and then reinvoking `input_handler`  
```{r, eval = FALSE}
# currprod_switch <- function(cropind, path = p_moddat) {
#   master_prod <- c("maize" = 2912004, "soy" = 203732)
#   currprod <- master_prod[cropind]
#   save(currprod, file = fp(path, "currprod.rda"))
#   return(currprod)
# }

@@

# mzto$conv[, sum(maize)]
# soyto$conv[, sum(soy)]

CRSobj <- CRS(mzto$inputs$sp$crs)
mztor <- dt_to_raster(mzto$conv, CRSobj)
soytor <- dt_to_raster(soyto$conv, CRSobj)
mzsoytor <- dt_to_raster(mzsoyto$conv, CRSobj)  # converges on same results

@@

basedt <- soyto$inputs$mask
```
<a href="#top">Back to top</a>

### Best Areas for Other Three Factors

Switch off for now
```{r, eval = FALSE}
# ybl <- list(yb1 <- c(1, 1))
# step <- 0.05
# cnames <- c("C", "BD", "COST")
# ps <- round(do.call(rbind, pareto_steps(cnames, step)), 2); head(ps)
# Yv = "conv_area"; Cv = "tot_C"; #BDv = "int_prior"; COSTv = "mu_cost"
# BDv = c(Yv, "int_prior"); COSTv = c(Yv, "mu_cost")
# wmu <- function(x, na.rm = na.rm) {
#   weighted.mean(x = x[, 2], w = x[, 1], na.rm = na.rm)
# }
# # Yst = sum; Cst = sum; BDst = mean; COSTst = mean
# Yst = sum; Cst = sum; BDst = wmu; COSTst = wmu
# 
# # crops <- list("maize", "soy", c("maize", "soy"))
# crops <- list(c("maize", "soy"))
# # croplnms <- list("maize", "soy", "both")
# croplnms <- list("both")
# # lapply(crops, function(x) targ[x])
# # lapply(crops, function(x) g[x])
# cbdc <- lapply(crops, function(x) {
#   a <- Sys.time()
#   print(paste("Starting run for", x, "at", a))
#   otab <- pareto(cnames, step = step, prod_targ = targ[x], 
#                  yblist = ybl, currprodmod = g[x], input_key = "ZA", 
#                  Yv = Yv, Cv = Cv, BDv = BDv, COSTv = COSTv, Yst = Yst, 
#                  Cst = Cst, BDst = BDst, COSTst = COSTst, todisk = TRUE, 
#                  silent = FALSE, ncl = 7)
#   load(fp(p_out, "bcode.rda"))
#   heatr <- heat(fp(p_out, bcode), basedt, todisk = TRUE) 
#   print(Sys.time() - a)
#   c("bcode" = bcode, otab, "heat" = heatr)
# })
# names(cbdc) <- croplnms
# 
# # cbdc <- lapply("ZA_20160215_071436_1558_16149", function(x) {
# #   bpath <- fp(p_out, x)
# #   load(fp(bpath, "impacts_tab.rda"))
# #   inlist <- lapply(unique(outtab$iter), function(x) {
# #     outtab[outtab$iter == x, ]
# #   })
# #   # load(fp(bpath, "optitab.rda"))
# #   optimal <- batch_stat(inlist, Yv = Yv, Cv = Cv, BDv = BDv, COSTv = COSTv, 
# #                         Yst = Yst, Cst = Cst, BDst = BDst, COSTst = COSTst)
# #   save(optimal, file = fp(bpath, "optitab.rda"))
# #   load(fp(bpath, "parms.rda"))
# #   heatr <- heat2(fp(p_out, x), basedt, todisk = TRUE, overwrite = TRUE) 
# #   list("bcode" = x, "optimal" = optimal, "params" = parms, "heat" = heatr)
# # })
# # names(cbdc) <- croplnms
# 
# # check for datasets where certain weights were removed from contention
# # clength <- t(sapply(cbdc, function(x) c(nrow(x$params), nrow(x$optitab))))
# # cbdcmz <- heat2(cbdc$maize, fp(p_out, cbdc$maize$bcode), basedt, todisk = TRUE)
# # cbdc$maize$heat <- cbdcmz

### Conservation interests versus agricultural interests
```{r, eval = FALSE}
ybl <- list(yb1 <- c(1, 1))
step <- 0.02
cnames <- c("Y", "COST")
ps <- round(do.call(rbind, pareto_steps(cnames, step)), 2)
# ps[which(rowSums(ps[, c(1, 3)]) == 0), ]
Yv = "conv_area"; Cv = "tot_C"
BDv = c(Yv, "int_prior"); COSTv = c(Yv, "mu_cost")
wmu <- function(x, na.rm = na.rm) {
  weighted.mean(x = x[, 2], w = x[, 1], na.rm = na.rm)
}
Yst = sum; Cst = sum; BDst = wmu; COSTst = wmu

crops <- list(c("maize", "soy"))
croplnms <- list("both")

ycost <- lapply(crops, function(x) {
  a <- Sys.time()
  print(paste("Starting run for", x, "at", a))
  otab <- pareto(cnames, step = step, prod_targ = targ[x], 
                  yblist = ybl, currprodmod = g[x], input_key = "ZA", 
                  Yv = Yv, Cv = Cv, BDv = BDv, COSTv = COSTv, Yst = Yst, 
                  Cst = Cst, BDst = BDst, COSTst = COSTst, todisk = TRUE, 
                  silent = FALSE, ncl = 7)
  load(fp(p_out, "bcode.rda"))
  heatr <- heat2(fp(p_out, bcode), basedt, todisk = TRUE) 
  print(Sys.time() - a)
  c("bcode" = bcode, otab, "heat" = heatr)
})
names(ycost) <- croplnms
# plot(ycost$both$optitab$Y, ycost$both$optitab$COST)

# fix because ran with heat2 not yet adjusted for improperly ordered csv files
ycostfix <- lapply(ycost, function(x) {  # x <- ycost$both
  if(nrow(x$params) > nrow(x$optitab)) {
    print(paste("fixing heat map for", x$bcode))
    heatfix <- heat2(fp(p_out, x$bcode), basedt, TRUE, TRUE)
  } else {
    heatfix <- NULL
  }
  heatfix
})
for(i in 1:length(ycost)) ycost[[i]]$heat <- ycostfix[[i]]

# ycost <- lapply("ZA_20160215_072118_1558_04246", function(x) {
#   bpath <- fp(p_out, x)
#   load(fp(bpath, "impacts_tab.rda"))
#   inlist <- lapply(unique(outtab$iter), function(x) {
#     outtab[outtab$iter == x, ]
#   })
#   optimal <- batch_stat(inlist, Yv = Yv, Cv = Cv, BDv = BDv, COSTv = COSTv, 
#                         Yst = Yst, Cst = Cst, BDst = BDst, COSTst = COSTst)
#   save(optimal, file = fp(bpath, "optitab.rda"))
#   load(fp(bpath, "parms.rda"))
#   heatr <- heat2(fp(p_out, x), basedt, todisk = TRUE, overwrite = TRUE) 
#   list("bcode" = x, "optimal" = optimal, "params" = parms, "heat" = heatr)
# })
# names(ycost) <- croplnms
# clength <- t(sapply(ycost, function(x) c(nrow(x$params), nrow(x$optitab))))

cnames <- c("C", "BD")
bdc <- lapply(crops, function(x) {
  a <- Sys.time()
  print(paste("Starting run for", x, "at", a))
  otab <- pareto(cnames, step = step, prod_targ = targ[x], 
                  yblist = ybl, currprodmod = g[x], input_key = "ZA", 
                  Yv = Yv, Cv = Cv, BDv = BDv, COSTv = COSTv, Yst = Yst, 
                  Cst = Cst, BDst = BDst, COSTst = COSTst, todisk = TRUE, 
                  silent = FALSE, ncl = 7)
  load(fp(p_out, "bcode.rda"))
  # heatr <- heat2(fp(p_out, bcode), basedt, todisk = TRUE) 
  print(Sys.time() - a)
  c("bcode" = bcode, otab, "heat" = heatr)
})
names(bdc) <- croplnms

# fix because ran with heat2 not yet adjusted for improperly ordered csv files
bdcfix <- lapply(bdc, function(x) {  # x <- ycost$both
  if(nrow(x$params) > nrow(x$optitab)) {
    print(paste("fixing heat map for", x$bcode))
    heatfix <- heat2(fp(p_out, x$bcode), basedt, TRUE, TRUE)
  } else {
    heatfix <- NULL
  }
  heatfix
})
for(i in 1:length(bdc)) bdc[[i]]$heat <- bdcfix[[i]]

# plot(bdc$both$optitab$C, bdc$both$optitab$BD)
# bdc3 <- c(bdc, bdc2)  # vestiges to show I forgot to do maize soy case
# bdc <- bdc3

# # Fix pareto tab
# load(fp(fp(p_out, bdc$both$bcode), "impacts_tab.rda"))
# inlist <- lapply(unique(outtab$iter), function(x) outtab[outtab$iter == x, ])
# outtabf <- batch_stat(inlist, Yv = Yv, Cv = Cv, BDv = BDv, COSTv = COSTv, 
#                       Yst = Yst, Cst = Cst, BDst = BDst, COSTst = COSTst)

# bdcfix <- lapply(bdc, function(x) {  # x <- bdc$maize
#   if(nrow(x$params) > nrow(x$optitab)) {
#     print(paste("fixing heat map for", x$bcode))
#     heatfix <- heat2(x, fp(p_out, x$bcode), basedt, todisk = TRUE)
#   } else {
#     heatfix <- NULL
#   }
#   heatfix
# })
# for(i in 1:length(bdc)) bdc[[i]]$heat <- bdcfix[[i]]

# bdc <- lapply("ZA_20160215_072332_1558_54465", function(x) {
#   bpath <- fp(p_out, x)
#   load(fp(bpath, "impacts_tab.rda"))
#   inlist <- lapply(unique(outtab$iter), function(x) {
#     outtab[outtab$iter == x, ]
#   })
#   # load(fp(bpath, "optitab.rda"))
#   optimal <- batch_stat(inlist, Yv = Yv, Cv = Cv, BDv = BDv, COSTv = COSTv, 
#                         Yst = Yst, Cst = Cst, BDst = BDst, COSTst = COSTst)
#   save(optimal, file = fp(bpath, "optitab.rda"))
#   load(fp(bpath, "parms.rda"))
#   heatr <- heat2(fp(p_out, x), basedt, todisk = TRUE, overwrite = TRUE) 
#   list("bcode" = x, "optimal" = optimal, "params" = parms, "heat" = heatr)
# })
# names(bdc) <- croplnms

# save(cbdc, ycost, bdc, file = fp(p_out, "mainresults1402.rda"))
save(ycost, bdc, file = fp(p_out, "mainresults1702.rda"))
```

### All 4 together
```{r, eval = FALSE}
step <- 0.05
cnames <- c("Y", "C", "BD", "COST")
ps <- round(do.call(rbind, pareto_steps(cnames, step)), 2)
ybdc <- lapply(crops, function(x) {
  a <- Sys.time()
  print(paste("Starting run for", x, "at", a))
  otab <- pareto(cnames, step = step, prod_targ = targ[x], 
                  yblist = ybl, currprodmod = g[x], input_key = "ZA", 
                  Yv = Yv, Cv = Cv, BDv = BDv, COSTv = COSTv, Yst = Yst, 
                  Cst = Cst, BDst = BDst, COSTst = COSTst, todisk = TRUE, 
                  silent = FALSE, ncl = 7)
  load(fp(p_out, "bcode.rda"))
  # heatr <- heat(fp(p_out, bcode), basedt, todisk = TRUE) 
  print(Sys.time() - a)
  c("bcode" = bcode, otab) #, "heat" = heatr)
})
names(ybdc) <- croplnms

# fix because ran with heat2 not yet adjusted for improperly ordered csv files
ybdcfix <- lapply(ybdc, function(x) {  # x <- ycost$both
  if(nrow(x$params) > nrow(x$optitab)) {
    print(paste("fixing heat map for", x$bcode))
    heatfix <- heat2(fp(p_out, x$bcode), basedt, TRUE, TRUE)
  } else {
    heatfix <- NULL
  }
  heatfix
})
for(i in 1:length(ybdc)) ybdc[[i]]$heat <- ybdcfix[[i]]

# ran because of fail on iteration for both (croplnms not properly compiled)
# bnames <- c("ZA_20160213_231906_17404_28678", "ZA_20160213_234959_17404_39818")
# ybdc <- lapply("ZA_20160215_072541_1558_17131", function(x) {
#   bpath <- fp(p_out, x)
#   load(fp(bpath, "impacts_tab.rda"))
#   inlist <- lapply(unique(outtab$iter), function(x) {
#     outtab[outtab$iter == x, ]
#   })
#   # load(fp(bpath, "optitab.rda"))
#   optimal <- batch_stat(inlist, Yv = Yv, Cv = Cv, BDv = BDv, COSTv = COSTv, 
#                         Yst = Yst, Cst = Cst, BDst = BDst, COSTst = COSTst)
#   save(optimal, file = fp(bpath, "optitab.rda"))
#   load(fp(bpath, "parms.rda"))
#   heatr <- heat2(fp(p_out, x), basedt, todisk = TRUE, overwrite = TRUE) 
#   list("bcode" = x, "optimal" = optimal, "params" = parms, "heat" = heatr)
# })
# names(ybdc) <- croplnms

# ybdc2 <- lapply(crops[3], function(x) {
#   a <- Sys.time()
#   print(paste("Starting run for", x, "at", a))
#   otab <- pareto(cnames, step = step, prod_targ = targ[x], 
#                   yblist = ybl, currprodmod = g[x], input_key = "ZA", 
#                   Yv = Yv, Cv = Cv, BDv = BDv, COSTv = COSTv, Yst = Yst, 
#                   Cst = Cst, BDst = BDst, COSTst = COSTst, todisk = TRUE, 
#                   silent = FALSE, ncl = 7)
#   load(fp(p_out, "bcode.rda"))
#   # heatr <- heat(fp(p_out, bcode), basedt, todisk = TRUE) 
#   print(Sys.time() - a)
#   c("bcode" = bcode, otab) #, "heat" = heatr)
# })
# names(ybdc2) <- croplnms[[3]]
# ybdc3 <- c(ybdc, ybdc2)  # vestiges to show I forgot to do maize soy case
# ybdc <- ybdc3

# heat maps
# ybdcheat <- lapply(ybdc, function(x) {  # x <- bdc$maize
#   print(paste("N params =", nrow(x$params), ": N optimal =",  nrow(x$optitab)))
#   heatfix <- heat2(x, fp(p_out, x$bcode), basedt, todisk = TRUE, 
#                    overwrite = TRUE)
#   heatfix
# })
# for(i in 1:length(ybdc)) ybdc[[i]]$heat <- ybdcheat[[i]]

# plot(ybdc$maize$heat)
# par(mfrow = c(1, 2))
# plot(ycost$maize$heat)
# plot(ycost$soy$heat)
# plot(ycost$both$heat)
# plot(bdc$both$heat)
# save(ybdc, cbdc, ycost, bdc, file = fp(p_out, "mainresults1502.rda"))
save(ybdc, ycost, bdc, file = fp(p_out, "mainresults1702.rda"))
# load(fp(p_out, "mainresults1702.rda"))
```

@@

fnames <- imp_sorter(fp(p_out, ybdc$both$bcode), inds = pure, fullnames = TRUE)
pure_r <- lapply(fnames, function(x) {  # x <- pure[1]
  DT <- cbind(fread(x), basedt[, .(x, y, convertible)])
  DTr <- dt_to_raster(DT, CRSobj)
})
# sapply(1:4, function(x) which(ps[, x] == 1))
# sum across crops and multiply by convertible areas
rs <- lapply(pure_r, function(x) calc(x[[1:2]], sum) * x[[3]])  # actual area
rs2 <- lapply(pure_r, function(x) calc(x[[1:2]], sum))  # conv pixels
# check
# sapply(rs, function(x) cellStats(x, sum))
# ybdc$both$optitab[ind %in% pure, Y]  # same, but C optimized out
# sapply(rs2, function(x) cellStats(x, sum))
# plot(pure_r[[3]])

# figure out overlaps between different pure objectives
pms <- expand.grid(rep(list(0:1), 4))[-1, ]  # logic grid
rownames(pms) <- 1:15
rs_over <- lapply(1:nrow(pms), function(x) {  # apply logic tests
  (rs2[[1]] == pms[x, 1]) & (rs2[[2]] == pms[x, 2]) & (rs2[[3]] == pms[x, 3]) &     (rs2[[4]] == pms[x, 4])
})
rs_overs <- stack(rs_over)

# legend to show class of overlap
pms$leg <- c("Y", "C", "YC", "Bd", "YBd", "BdC", "YBdC", "Ct", 
             "YCt", "CCt", "YCCt", "BdCt", "YBdCt", "CBdCt", 
             "YCBdCt")

# frequency of overlaps in different categories
# sum(pms[c(1, 3, 5, 7, 9, 11, 13, 15), "hist"])
pms$hist <- sapply(1:nlayers(rs_overs), function(x) {
  round(cellStats(rs_overs[[x]] * pure_r[[1]]$convertible, sum), 1)
})

# legend color
pms$col <- c("dodgerblue3", "goldenrod2", "tomato1", "yellow", 
             rep("tomato1", 2), "red3", "deepskyblue1", rep("tomato1", 2),
             rep("red3", 5))

# recode with unique number for overlap class, collapse to RasterLayer, 
# simplify classes for plotting
rs_over_rc <- stack(lapply(1:length(rs_over), function(x) rs_over[[x]] * x))
rs_over_rc <- calc(rs_over_rc, sum)
# plot(rs_over_rc == 6)
rclmat <- cbind(0:15, c(0, 1, 3, 5, 4, 5, 5, 6, 2, 5, 5, 6, 5, 6, 6, 6))
leg2 <- c("Yield", "Cost", "Carbon", "Biodiversity", "2 overlap", "3+ overlap")
rs_over_rc2 <- raster::reclassify(rs_over_rc, rclmat)

# plot(1:2, pch = 20, cex = 3, col = c("yellow", "yellow2"))

@@

# select out corresponding impact statistics, summarize
pure2 <- unlist(lapply(pure, function(x) c(x, x + 1)))
vars <- c("iter", "conv_area", "tot_C", "fpa_conv", "mu_cost", "rarity",
          "priority",  "int_prior", "int_mean")
conv_stats <- selected_impacts(pure, fp(p_out, ybdc$both$bcode))

# rescale for common plot
svec <- c(100000, 10000000, 1000, 1, 0.1, 0.1, 0.1, 0.1)  # rescale factor
conv_stats_n <- sweep(as.matrix(conv_stats)[, -1], MARGIN = 2, svec, "/")
conv_stats_n <- conv_stats_n[, c(1, 4, 2, 6:ncol(conv_stats_n), 3)]

# Plots
# Panel A
# cols <- RColorBrewer::brewer.pal(11, "RdYlBu")
# cols <- colorspace::diverge_hsv(n = 11)
# colsi <- sapply(c(0.5, 0.75, 1), function(x) rgb(1, 1, 0.9, alpha = x))
cols <- c("dodgerblue3", "deepskyblue1", "goldenrod2", "yellow", "tomato1",
          "red3")
# plot(1:6, pch = 20, cex = 3, col = cols)

tiff(fp(p_figures, "single_priorities.tif"), height = 3, width = 8, 
     units = "in", res = 300)
par(mfrow = c(1, 3))
imp_plot2(dtr = rs_over_rc2, impacts = i1, fpath = p_figures, 
          fnm = "pure_overlap", cexscale = 0.5, ftitle = "", crops = leg2, 
          stats = FALSE, cols = cols, hold = TRUE, marg = c(0, 0, 0, 0))

# Panel B
# totf <- cellStats(rs_over_rc > 0, sum)
par(mar = c(7, 4, 2, 2))
bp <- barplot(pms$hist / sum(pms$hist) * 100, ylim = c(0, 25), las = 2, 
              col = pms$col, mgp = c(2, 0.25, 0), tcl = -0.2, 
              ylab = "% converted area")
axis(side = 1, at = bp, labels = pms$leg, las = 2, mgp = c(2, 0.25, 0), 
     tcl = -0.2)
# TeachingDemos::subplot( 
#   bp <- barplot(pms$hist / sum(pms$hist) * 100, ylim = c(0, 25), las = 2, 
#                 col = pms$col, mgp = c(2, 0.25, 0), tcl = -0.2, 
#                 ylab = "% converted pixels", names.arg = pms$leg), 
#   x=grconvertX(c(0.1,0.45), from='npc'),
#   y=grconvertY(c(0.6,1), from='npc'),
#   type='fig', pars=list(mar=c(3,3,0,0) + 0.1))

# Panel C
# barplot(conv_stats_n)
blabs <- c("Area", "Time", "Carbon", "Priority", "Priority/intactness", 
           "Intactness", "Forest reserves")
# blabs <- sub(':', '\n', blabs)
tlabs <- c(expression(10^5~"km"^2), "hours", expression(10^7~"tons"), 
           rep("X10", 3), expression(10^3~"km"^2))
bp <- barplot(conv_stats_n, beside = TRUE, ylim = c(0, 14), las = 2, 
              col = pms$col[c(1, 2, 4, 8)], names.arg = rep("", length(blabs)), 
              ylab = "Impact*", mgp = c(2, 0.25, 0), tcl = -0.2)
text(x = bp[2, ] - 0.4, y = rep(-0.3, length(bp[1, ])), adj = 1, 
     labels = blabs, xpd = NA, srt = 90)
text(x = bp[3, ] + 0.4, y = rep(-0.3, length(bp[3, ])), adj = 1, 
     labels = tlabs, xpd = NA, srt = 90, cex = 0.8)
dev.off()

@@

scens_rs2 <- lapply(scens_r, function(x) calc(stack(x[[1:2]]), sum))
# plot(scens_rs2[[1]] + scens_rs2[[2]])
# check
# round(sapply(scens_rs2, function(x) {
#   cellStats(x * scens_r[[1]]$convertible * 100, sum)
# }))
# cstats$conv_area

>>>>

setwd("~/Dropbox/publications/zambiaToff/private/zambiaToff/")
p_root <- getwd()
p_demand <- fp(p_root, "external/input_devel/demand/")
p_mod <- fp(p_root, "agroEcoTradeoff")
p_moddat <- fp(p_mod, "external/data/ZA")
p_figures <- full_path(p_root, "paper/figures/")
p_other <- fp(p_root, "external/input_devel/other/")
# p_roads <- fp(p_root, "external/input_devel/roads")
# p_roads2 <- paste0("/Users/lestes/Dropbox/data/zari/infrastructure/zambia/", 
#                    "rda_dump/Final Shape files RDA/")
p_out <- fp(p_mod, "external/output")
```

```{r, eval = FALSE}
# roads
mgrid <- raster(fp(p_moddat, "ZA-mask.tif"))
load(fp(p_mod, "external/data/ZA/parks_roads.rda"))

@@

@@

Running the model individually for each crop and for both crops.
```{r, eval = FALSE}
setwd(p_mod)
path <- "external/data/ZA"

# gaps 
cp <- c("maize" = 2912004, "soy" = 203732)  # current production
gapper <- function(cp, gaps, pct) ((((cp * gaps) - cp) * pct) + cp) / cp
mzgap <- 4.43 / 2.3 
soygap <- 3.4 / 2
g <- gapper(cp, c(mzgap, soygap), 0.25)  # assume 50% closed on current land
targ <- c("maize" = 3, "soy" = 9)  # targets given g
targs <- targets(targ, cp, g)

@@

# rasters
CRSobj <- CRS(mzto$inputs$sp$crs)
mztor <- dt_to_raster(mzto$conv, CRSobj)
soytor <- dt_to_raster(soyto$conv, CRSobj)
mzsoytor <- dt_to_raster(mzsoyto$conv, CRSobj)  # converges on same results

@@

basedt <- soyto$inputs$mask
crops <- list(c("maize", "soy"))

```{r, eval = FALSE}
load(fp(p_out, "mainresults1702.rda"))
```

@@

fnames <- imp_sorter(fp(p_out, ybdc$both$bcode), inds = pure, fullnames = TRUE)
pure_r <- lapply(fnames, function(x) {  # x <- pure[1]
  DT <- cbind(fread(x), basedt[, .(x, y, convertible)])
  DTr <- dt_to_raster(DT, CRSobj)
})

# sum across crops and multiply by convertible areas
rs <- lapply(pure_r, function(x) calc(x[[1:2]], sum) * x[[3]])  # actual area
rs2 <- lapply(pure_r, function(x) calc(x[[1:2]], sum))  # conv pixels
names(rs2) <- cnames
# check
# sapply(rs, function(x) cellStats(x, sum))
# ybdc$both$optitab[ind %in% pure, Y]  # same, but C optimized out
# sapply(rs2, function(x) cellStats(x, sum))
# plot(pure_r[[3]])

# figure out overlaps between different pure objectives
pms2a <- expand.grid(rep(list(0:1), 4))[-1, ] 
pms2b <- pms2a[which(rowSums(pms2a) == 2), ]
pms2b$cl <- c("YC", "YBd", "CBd", "YCt", "CCt", "BdCt")
rownames(pms2b) <- 1:6

# pairwise overlaps
rs_over <- lapply(1:nrow(pms2b), function(x) {  # apply logic tests
  calc(stack(rs2[which(pms2b[x, ] == 1)]), sum)
})
names(rs_over) <- pms2b$cl

# Jaccard Index of overlaps
rs_over_a <- sapply(1:length(rs_over), function(x) { # x <- 4
  sapply(1:2, function(y) {  # y <- 3
    r <- rs_over[[x]] == y
    round(cellStats(r * pure_r[[1]]$convertible, sum), 1)
  })
})
pms2b$JS <- round(rs_over_a[2, ] / colSums(rs_over_a), 3)

# calculate nearest neighbor distance between each version, using spatstat 
# nncross
zam_owin <- owin(xrange = bbox(zambia)[1, ], yrange = bbox(zambia)[2, ],
                 unitname = "meter")
which1 <- function(x) x == 1  # selector function for r to xy
rsover_nn <- lapply(1:nrow(pms2b), function(x) {  # apply logic tests; x = 2
  ind <- which(pms2b[x, 1:4] == 1)
  rl <- rs2[ind]
  rxy <- lapply(rl, function(x) rasterToPoints(x, fun = which1))
  pps <- lapply(rxy, function(x) {
    ppp(x = x[, 1], y = x[, 2], window = zam_owin)
  })
  # reorder to find which has most points, to put that in as X
  reord <- sort(sapply(pps, function(x) x$n), decreasing = TRUE)
  ppnn <- nncross(pps[[names(reord)[1]]], pps[[names(reord)[2]]])
})
pms2b$NND <- round(sapply(rsover_nn, function(x) mean(x$dist))) / 1000

cols_tr <- c(rgb(1, 0, 0), rgb(0, 0, 1), rgb(0, 0.75, 1), rgb(1, 0.75, 0))
plot(1:4, cex = 3, pch = 20, col = cols_tr)

# impact table

@@

# select out corresponding impact statistics, summarize
conv_stats <- selected_impacts(pure, fp(p_out, ybdc$both$bcode))
impsr <- lapply(c(2, 5, 3, 7:9, 4), function(x) conv_stats[[x]])

# Plot setup
m1 <- do.call(cbind, lapply(1:4, function(x) matrix(rep(x, 35), 5, 7)))
m2 <- matrix(rep(5, 20), 4, 5)
m3 <- do.call(cbind, lapply(6:12, function(x) matrix(rep(x, 12), 4, 3)))
lmat <- rbind(m1, cbind(rep(5, 4), m2, m3, rep(13, 4)))

# plot(1:10, ylab = ylabs[2])
# ylabs <- c("Jaccard Index", 
ylabs <- c(expression(paste("Converted area (", 10^5, " ", km^2, ")")), 
           "Hours", "C loss (Mt)", "Priority", "Intactness/priority",
           "Intactness", expression(paste("FR converted (ha"^2, ")")))
# yscale <- c(1, 10^5, 1, 100000, 1, 1, 1, 1)
yscale <- c(10^5, 1, 100000, 1, 1, 1, 1)
ftits <- list("Y 100%", "C 100%", "Biod 100%", "Cost 100%")
leg <- c("Converted")

yaxes <- list(seq(0, 14, 2), seq(0, 7, 0.5),               
              seq(0, 1100, 100), seq(0, 0.12, 0.02), seq(0, 0.6, 0.1), 
              seq(0, 1, 0.1), seq(0, 6500, 500))
bcols <- c(list(c(cols_tr[1], cols_tr[2], cols_tr[1], cols_tr[2], 
                  cols_tr[3])), lapply(1:7, function(x) rep("black", 4)))

# plot
tiff(fp(p_figures, "single_priorities2.tif"), height = 3.5, width = 7, 
     units = "in", res = 300)
l <- layout(mat = lmat)
# layout.show(l)

# map plots
for(i in 1:4) { # i <- 1
  imp_plot2(rs2[[i]], impacts = i1, fpath = p_figures, fnm = "bob",
            crops = leg, ftitle = ftits[[i]], col = cols_tr[[i]], 
            legend = TRUE, hold = TRUE, stats = FALSE, cexscale = 0.4, 
            marg = rep(0, 4))
}

# impact plots
mgp <- c(1.6, 0.25, 0)
par(mar = c(4, 3, 0, 0))
with(pms2b, {
  plot(NND, JS, col = cols_tr[c(2, 3, 3, 4, 4, 4)], pch = 16, cex = 1.5, 
       axes = FALSE, xlab = "", ylab = "", ylim = c(0, 0.3))
  points(NND, JS, col = cols_tr[c(1, 1, 2, 1, 2, 3)], pch = 20, cex = 1)
  axis(1, at = seq(0, 230, 20), cex.axis = 0.6, las = 2, mgp = mgp, 
       tcl = -0.2)
  axis(2, at = seq(0, 0.3, 0.05), cex.axis = 0.6, las = 2, mgp = mgp, 
       tcl = -0.2)
  mtext(text = "NN Distance (km)", side = 1, line = 1, cex = 0.45)
  mtext(text = "Jaccard Index", side = 2, line = 1.25, cex = 0.45)
})
mgp <- c(1, 0.25, 0)
for(i in 1:7) {
  v <- impsr[[i]] / yscale[i]
  b <- barplot(impsr[[i]] / yscale[i], las = 2,  col = cols_tr, 
               mgp = c(1.5, 0.25, 0), tcl = -0.2, yaxt = "n", 
               ylim = range(yaxes[[i]]), ylab = ylabs[i], cex.axis = 0.5,
               cex.lab = 0.7)
  axis(2, at = yaxes[[i]], cex.axis = 0.6, las = 2, mgp = mgp, 
       tcl = -0.2)
}
dev.off()

@@

scens_rs2 <- lapply(scens_r, function(x) calc(stack(x[[1:2]]), sum))
names(scens_rs2) <- paste0("w", 1:length(scens_rs2))
